---
title: "Course Project - Guess Mean Shiny Application"
author: "Silverio Neves"
date: "8 de Novembro de 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)

```

## Shiny Application Goal


The goal of the application is to have the maximum possible score guessing the mean using a tolerance.

- The user sets the guess mean and selects the tolerance.
- The computer generates randomly 10 numbers between 1 and 100
- The computer calculates the mean and compares to guess and tolerance
- To have no zero points the mean needs to be in the interval of the guess mean +/- tolerance.
- If the tolerance select was 1, the user obtain the maximum score of 100. 60 points for tolerance 5 and 20 points for tolerance 10.
- The computer attributes the user score based on tolerance selected 

## User Interface

```{r ui}
shinyUI(pageWithSidebar(
        headerPanel("Guess Game"),
        sidebarPanel(
                numericInput('mu', 'Select your Guess (1<=mean<=100)',value = 49, min = 1, max = 100, step = 1),
                radioButtons("tol", "Select your tolerance",
                              c("1 = 100 points" = 1,
                                "5 = 60 points" = 5,
                                "10 = 20 points" = 10),
                             selected = 10),
                hr(),
                tags$b(textOutput("gen1")),
                tags$i(textOutput("gen2"))
        ),
        mainPanel(
                tags$b(textOutput("txt1")),
                tags$b(textOutput("txt2")),
                hr(),
                plotOutput('newplot'),
                hr(),
                tags$b(textOutput("score"))
                
        )
))

```
The user selects in the side panel the guess mean and tolerance to see results on the right with text and graphic. 

## User Iterface

Your Guess was mean = 49 and tolerance = 10
```{r server}
        rdf <- data.frame(x=1:10, y = sample(1:100,10))
        m <- mean(rdf$y)
        mu <- 49
        tol <- 10
        plot(x = rdf$x, y=rdf$y, col = "darkgreen", pch = 12,
                     xlab = "10 numbers genereated by computer",
                     ylab = "Numbers value 1-100")
              abline(h = m, col = "darkblue", lty = 1)
              abline(h = (mu+tol), col ="red", lty=3)
              abline(h = (mu-tol), col ="red", lty=3)
              abline(h = mu, col ="red", lty=2)
              if (m >= (mu-tol) & m<= (mu+tol)){
                     if (tol == 1) s <- 100 else{
                               if(tol == 5) s <- 60 else s<- 20
                }} else s <- 0

```
Your score is **```r s```**

On the left side (side panel) appears all randomly generated numbers : ```r rdf$y```

## Conclusions

This simple application can demonstrate how the Shiny is very suitable to do interactive graphics to present our results in conjugation with others stuffs to help in this work.

